**Urban mobility in Latin America after COVID-19**

### 2024-01-19 manuscript/manuscript.qmd
rm old versions

>>>>

Make it general

• Context and importance: Focus on urban spaces, livability, resilience and recov- ery - links to public health and climate change\
• Previous work\
• Gap: focus on medium - long term impacts of COVID-19 / recovery - explain why focus on South America (global south could be Africa too, or less developed countries in Asia).\
• Aim:
